Revealing Benefits, Costs, and Tradeoffs of Spatial Management Arrising from Coupled Economic and Ecological Dynamics in Marine Systems

### 2023-05-23 presentations/tunacamp_slides.qmd
slides testing for tunacamp

---
title: "Revealing Benefits, Costs, and Tradeoffs of Spatial Management Arrising from Coupled Economic and Ecological Dynamics in Marine Systems"
author: "Dan Ovando"
format:
  revealjs:
    embed-resources: true
editor: visual
---

## Quarto

Quarto enables you to weave together content and executable code into a
finished presentation. To learn more about Quarto presentations see
<https://quarto.org/docs/presentations/>.

## Bullets

When you click the **Render** button a document will be generated that
includes:

-   Content authored with markdown
-   Output from executable code

## Code

When you click the **Render** button a presentation will be generated
that includes both content and the output of embedded code. You can
embed code like this:

```{r}
1 + 1
```

>>>>

---
title: "Revealing Benefits, Costs, and Tradeoffs of Spatial Management Arrising from Coupled Economic and Ecological Dynamics in Marine Systems"
author: "Dan Ovando"
format:
  revealjs:
    embed-resources: false
---

## Complexity Matters!

![](imgs/complexity.png)
